Binning Strategies and Related Loss for Large Data

### 2015-04-09 Paper.Rnw
FreqLossDisplay-1

# Plot with Orginal Frequencies
p1 <- qplot(binxs, binys, geom="tile", fill=binfreq, data=binoutFreqGroups[[1]],
            main="No Freq Binning") +
  xlab("") + ylab("")+
  scale_fill_gradient(low="#56B1F7", high="#132B43") + 
  theme_bw() + theme(legend.position="bottom",aspect.ratio=1,
                     panel.grid= element_blank())
# Plot with Binned Frequencies
p2 <- qplot(binxs, binys, geom="tile", fill=freqgroup, data=binoutFreqGroups[[1]],
            main="Standard Freq Binning") +
    xlab("") + ylab("")+
  scale_fill_gradient(low="#56B1F7", high="#132B43", guide="legend",
                      breaks=unique(binoutFreqGroups[[1]]$freqgroup)) + 
  theme_bw() + theme(legend.position="bottom",aspect.ratio=1,
                     panel.grid= element_blank())
# Plot with Quantile Binned Frequencies
p3 <- qplot(binxs, binys, geom="tile", fill=freqgroup, data=binoutQuantFreqGroups[[1]],
            main="Quantile Freq Binning") +
    xlab("") + ylab("")+
  scale_fill_gradient(low="#56B1F7", high="#132B43", guide="legend", breaks=unique(binoutQuantFreqGroups[[1]]$freqgroup)) + 
  theme_bw() + theme(legend.position="bottom",aspect.ratio=1,
                     panel.grid= element_blank())
# Plot with LogCount Binned Frequencies
p4 <- qplot(binxs, binys, geom="tile", fill=freqgroup, data=binoutLogFreqGroups[[1]],
            main="Log Freq Binning") +
    xlab("") + ylab("")+
  scale_fill_gradient(low="#56B1F7", high="#132B43", guide="legend", breaks=unique(binoutLogFreqGroups[[1]]$freqgroup)) + 
  theme_bw() + theme(legend.position="bottom",aspect.ratio=1,
                     panel.grid= element_blank())

>>>>

# Plot with Orginal Frequencies
p1 <- qplot(binxs, binys, geom="tile", fill=binfreq, data=binoutFreqGroups[[1]],
            main="No Freq Binning") +
  xlab("") + ylab("")+
  scale_fill_gradient(low="#56B1F7", high="#132B43") + 
  theme_bw() + theme(legend.position="bottom",aspect.ratio=1,
                     panel.grid= element_blank())
# Plot with Binned Frequencies

p2 <- qplot(binxs, binys, geom="tile", fill=freqgroup, data=binoutFreqGroups[[1]],
            main="Standard Freq Binning") +
    xlab("") + ylab("")+
  scale_fill_gradient(low="#56B1F7", high="#132B43", 
                      guide = guide_legend(label.position="bottom", label.hjust=0.5),
                      breaks=unique(binoutFreqGroups[[1]]$freqgroup),
                      labels=unique(binoutFreqGroups[[1]]$freqlabel)) + 
  theme_bw() + theme(legend.position="bottom",aspect.ratio=1,
                     legend.key.width = unit(2, "cm"),
                     panel.grid= element_blank())

# Plot with Quantile Binned Frequencies
p3 <- qplot(binxs, binys, geom="tile", fill=freqgroup, data=binoutQuantFreqGroups[[1]],
            main="Quantile Freq Binning") +
    xlab("") + ylab("")+
  scale_fill_gradient(low="#56B1F7", high="#132B43", guide="legend", breaks=unique(binoutQuantFreqGroups[[1]]$freqgroup)) + 
  theme_bw() + theme(legend.position="bottom",aspect.ratio=1,
                     panel.grid= element_blank())
# Plot with LogCount Binned Frequencies
p4 <- qplot(binxs, binys, geom="tile", fill=freqgroup, data=binoutLogFreqGroups[[1]],
            main="Log Freq Binning") +
    xlab("") + ylab("")+
  scale_fill_gradient(low="#56B1F7", high="#132B43", guide="legend", breaks=unique(binoutLogFreqGroups[[1]]$freqgroup)) + 
  theme_bw() + theme(legend.position="bottom",aspect.ratio=1,
                     panel.grid= element_blank())
